\vspace{-3em} \includegraphics[width=.1\textwidth]{Figures/logo.png} \\ \includegraphics[width=4cm]{Figures/logotext.png} \\

### 2014-10-09 report/article_4.tex
new report header

\renewcommand{\sectionmark}[1]{\markright{\spacedlowsmallcaps{summerdatachallenge}}} % The header for all pages (oneside) or for even pages (twoside)
%\renewcommand{\subsectionmark}[1]{\markright{\thesubsection~#1}} % Uncomment when using the twoside option - this modifies the header on odd pages
\lehead{\mbox{\llap{\small\thepage\kern1em\color{halfgray} \vline}\color{halfgray}\hspace{0.5em}\rightmark\hfil}} % The header style

@@

\maketitle % Print the title/author/date block

@@

@@

\setlength{\intextsep}{0em}
\begin{wrapfigure}{R}{.3\textwidth}
%\vspace{-1em}
\centering
\includegraphics[width=.28\textwidth]{Figures/overview.png}
%\vspace{-1em}
\caption{ Mapped house sales, brightness is proportional to price.}
\end{wrapfigure}

>>>>

%\renewcommand{\sectionmark}[1]{
\markright{\spacedlowsmallcaps{summerdatachallenge}}
%} % The header for all pages (oneside) or for even pages (twoside)
%\renewcommand{\subsectionmark}[1]{\markright{\thesubsection~#1}} % Uncomment when using the twoside option - this modifies the header on odd pages
\lehead{\mbox{\llap{\small\thepage\kern1em\color{halfgray} \vline}\color{halfgray}\hspace{0.5em}\rightmark\hfil}} % The header style

@@

% \maketitle % Print the title/author/date block

@@

% Make header in inkscape?
\begin{figure}[width=\textwidth]
\vspace{-3em}
\centering
\includegraphics[width=.7\textwidth]{Figures/header2.pdf}
\vspace{.5em}
\end{figure}

%suppres headers
\thispagestyle{plain}

@@

\setlength{\intextsep}{0em}
\begin{wrapfigure}{R}{.3\textwidth}
%\vspace{-1em}
\centering
\includegraphics[width=.28\textwidth]{Figures/overview.png}
\vspace{-1em}
\caption*{ A map of the house prices dataset (brightness is proportional to
  price and density).}
\end{wrapfigure}
